% LaTeX file for resume 
% This file uses the resume document class (res.cls)

\documentclass{article}
\usepackage{fancyhdr} 
\usepackage{nameref}
\usepackage{float}
\usepackage[margin=1in,headheight=13.6pt]{geometry}
\usepackage[plainpages=false,pdfpagelabels]{hyperref}
%\usepackage{algorithm}
%\usepackage{algorithmic,algorithmic-fix}
\usepackage[english]{babel}
\usepackage[latin1]{inputenc}
\usepackage{latexsym}
\usepackage{amsmath,amsthm}
\usepackage{amsfonts}
\usepackage{epsfig}
\usepackage{amssymb}
\usepackage{tabularx}
\usepackage{graphicx,epsfig,psfrag,pstricks}
\usepackage{eso-pic}
\usepackage{pdflscape}
\usepackage{hyperref}
\usepackage{flafter}
\usepackage[mathscr]{euscript}
\usepackage{array, lscape}
\usepackage{pb-diagram}
\usepackage{harvard}
\usepackage{titlesec}

\setlength\parindent{0pt}

\titleformat{\subsection}
  {\normalfont\large\bfseries}{\thesection}{1em}{}[{\titlerule[0.8pt]}]

\usepackage[all]{hypcap} 
\usepackage[latin1]{inputenc} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 
\setlength{\textheight}{9.5in} % increase text height to fit on 1-page 
%\markright{Mauricio Romero - Economics Department (PhD Application)}
%\pagestyle{myheadings}
\pagestyle{fancy}
\fancyhf{}
\fancyhead[R]{{\textbf{SHUNSUKE HORI}}\\
{UNIVERSITY OF CALIFORNIA, SAN DIEGO}}

 
\begin{document} 
\thispagestyle{empty}
\begin{center}
{\Large \textbf{SHUNSUKE HORI}}\\
\vspace{0.1cm}
{\Large ECONOMICS DEPARTMENT}\\
\vspace{0.1cm}
{\Large UNIVERSITY OF CALIFORNIA, SAN DIEGO}\\
\end{center}
	
			        % line after name
\vspace{-0.7cm}			        
\begin{center}
\line(1,0){500}
\end{center}

\begin{tabularx}{\textwidth}{XXXX}
Placement Director &	James Andreoni	& (858) 534-3832 & \href{mailto:andreoni@ucsd.edu}{andreoni@ucsd.edu}  \\
Placement Coordinator &	Andrew Flores &	(858) 534-1867 & \href{mailto:econ-jobmarket@ucsd.edu}{econ-jobmarket@ucsd.edu}
\end{tabularx} 



\noindent \subsection*{CONTACT INFORMATION}


\begin{minipage}{0.45\textwidth}
\begin{tabularx}{\textwidth}{XX}
Department of Economics \\
University of California, San Diego \\
9500 Gilman Drive \\
La Jolla, CA 92093-0508 \\
\end{tabularx} 
\end{minipage}	
\begin{minipage}{0.45\textwidth}
\begin{tabularx}{\textwidth}{XX}
Phone: (858) 610-7632 \\
Fax: (858) 534-7040 \\
Email: \href{mailto:shhori@ucsd.edu}{shhori@ucsd.edu} \\
Website: \mbox{\url{https://shunsuke-hori.github.io/index.html}} \\
\end{tabularx} 
\end{minipage}

\subsection*{EDUCATION}  

\begin{tabularx}{\textwidth}{XX}

University of California - San Diego, California, U.S.A. & PhD Candidate in Economics, 2023 (expected) \\  
 & \textbf{Committee}: \\
 & David Lagakos (co-chair) \\
 & Valerie A. Ramey (co-chair) \\
 & Alexis Akira Toda \\
 & Titan Alon \\
 & Munsueb Lee \\
 & Ulrike Schaede \\
 \\

Graduate School of University of Tokyo, Tokyo, Japan & (only finished course work) \\
%Universidad de los Andes, Bogotá, Colombia & Minor in Environmental Studies and Biodiversity, 2010 \\
Keio University, Tokyo, Japan &  B.A. Economics (Summa Cum Laude), 2015 \\  
\end{tabularx}\\


\subsubsection*{REFERENCES}


\begin{tabularx}{\textwidth}{XXXX}
David Lagakos & Boston University & \href{mailto:lagakos@bu.edu}{lagakos@bu.edu} & (617) 353-8903 \\
Valerie A. Ramey & UC San Diego & \href{mailto:vramey@ucsd.edu}{vramey@ucsd.edu} & (858) 534-2388\\
Alexis Akira Toda & UC San Diego & \href{mailto:atoda@ucsd.edu}{atoda@ucsd.edu} & (858) 534-3383 \\
\end{tabularx}\\



\subsection*{FIELDS OF INTERESTS}
\begin{tabularx}{\textwidth}{XX}
Macroeconomics, Macro Labor \\
\end{tabularx}\\


 
\subsection*{RELEVANT POSITIONS HELD}

\begin{tabularx}{1.2\textwidth}{lXX}
    Research Assistant & UCSD (Prof. Mark Jacobsen) &  2022 \\
    Intern & International Monetary Fund (Alexis Meyer Cirkel) & 2021 \\
    Lead Developer & QuantEcon &  2017 \\
    Research Assistant & University of Tokyo (Prof. Tomohiro Hirano) &  2015-2017 \\
\end{tabularx}
\\

\subsection*{FELLOWSHIP, HONORS, AND AWARDS}

\begin{tabularx}{\textwidth}{XX}
    Walter P. Heller Memorial Prize. 2020. University of California - San Diego.\\
    Summer 2019 GSA Travel Grant. 2019. University of California - San Diego.\\
    Graduate Student research funding. 2019. University of California - San Diego.  \\
    Japan-IMF Scholarship. 2017-2019. Japan IMF Scholarship Program for Advanced Studies. \\
\end{tabularx}
\\

\subsection*{WORKING PAPERS}


``The Secular Decline in Aggregate Hours Worked in
Japan: A Reinterpretation (Job Market Paper)'' \\
\begin{center}
\begin{minipage}{0.9\linewidth}
    \textit{\textbf{Abstract:}
        Average hours worked per adult in Japan fell by around one third over the last half-century. The leading explanation focuses on government policies that distort labor supply decisions. This paper provides a new interpretation that stresses the role of income effects in preferences. Through the lens of a model of the market and home sectors and using non-homothetic preferences, I show that the main driver of Japan's decline in hours worked is income effects, rather than labor-market distortions or population aging. The model predicts that average hours of leisure will rise and home-production hours will remain roughly constant over the period, which is consistent with evidence from time-use surveys. An alternative calibration based on only labor market distortions counterfactually predicts that home production hours will rise.} \\
\end{minipage}
\end{center}

\subsection*{RESEARCH IN PROGRESS}

\begin{tabularx}{\textwidth}{XX}
``Generational war on inflation: Optimal inflation rates for the young and the old'' Joint with Ippei Fujiwara and Yuichiro Waki \\
``Human capital and Technology Diffusion:
Expanding the Discussion of Industrial Policy'' Joint with Alexis Meyer Cirkel\\
``Hysteresis in Hours Worked''\\
\end{tabularx}
\\

\subsection*{TEACHING EXPERIENCE}


\subsubsection*{As teaching assistant at UC San Diego}

\begin{tabularx}{\textwidth}{lXX}
    Data Analytics for the Social Sciences &Prof. David Arnold& Spring 2022  \\
    Short Run Macroeconomics &Prof. James Hamilton & Winter 2022 \\
    Long Run Macroeconomics  &Prof. Titan Alon & Fall 2021\\
    Long Run Macroeconomics  &Prof. Giacomo Rondina & Spring 2021\\
    Long Run Macroeconomics &Prof. Titan Alon& Fall 2020  \\
    Graduate Macroeconomics C &Prof. Johannes Wieland& Spring 2020 \\
    Graduate Macroeconomics B &Prof. Giacomo Rondina & Winter 2020\\
\end{tabularx} \\
\\

\subsection*{PROFESSIONAL ACTIVITIES}

\subsubsection*{Presentations}
\begin{tabularx}{\textwidth}{lX}
2019 & Summer Workshop on Economic Theory
\end{tabularx}

\subsubsection*{Conference Participation}
\begin{tabularx}{\textwidth}{lX}
2019 & Economics of Artificial Intelligence\\
2014 & Summer Workshop on Economic Theory\\
\end{tabularx}

\subsubsection*{Referee Service}
\begin{tabularx}{\textwidth}{l}
\textit{Review of Economic Dynamics}\\
\end{tabularx}

\subsection*{COMPUTATIONAL SKILLS}
\begin{tabularx}{\textwidth}{lX}
Language: Julia, Python, Matlab, R, Stata
\end{tabularx}

\subsection*{OTHER INFORMATION}
\begin{tabularx}{\textwidth}{lX}
Citizenship: Japan \\
Date of birth: May 18th, 1992 \\
\end{tabularx}

%\section{REFERENCES}
%Alejandro Gaviria \\
%Dean of Economics - Universidad de los Andes \\
%Tel. 57-1-3324493 \\
%agaviria@uniandes.edu.co \\
%
%
%Alvaro Riascos \\
%Associate Professor - Universidad de los Andes \\
%Quantil S.A.S. CEO \\
%Tel. 57-3106791459 \\
%ariascos@gmail.com \\
       
 

\end{document}